Boosting Higgs Pair Production in the $b\bar{b}b\bar{b}$ Final State with Multivariate Techniques

### 2015-12-07 paper/sec-analysis.tex
More work on the paper

In section we describe our analysis strategy.
%
First of all, we discuss the settings
for jet clustering  and the strategy for $b$-tagging.
%
Then we discuss the categorisation of events in different
topologies and how to prioritise among them.
%
We motivate our choice of analysis cuts by comparing signal and background
for representative kinematical distributions.
%
Finally, we describe the simulation of PU and validate
the PU subtraction strategy that we adopt.

@@

  These subjets are constructed by reclustering the constituents
  of a large-$R$ jet, again with  anti-$k_T$ algorithm,
  but this time with a smaller radius parameter, namely
  $R=0.3$.
 %
  These small-$R$ subjets will be the main input for
  $b$-tagging in the boosted category.
  %
  They are required to satisfy $p_T > 50$~GeV and $|\eta|<2.5$.
  %
\end{itemize}

In addition, we have
also explored the possible improvements
in the analysis from the use
of variable-$R$ jets~\cite{Krohn:2009zg}, but found that these made
a small difference as compared to fixed-$R$ jets.
%
This is not unexpected, since variable-$R$ jets are more suitable when
the degree of boost of the final state being reconstructed can span
a wide range~\cite{Cacciari:2008gd}, such as in heavy resonance searches~\cite{Aad:2015fna},
where where the degree of boost of the final state
is {\it a priori} unknown.

@@

  %
  If a small-$R$ jet has at least one $b$-quark among their constituents,
  it will be tagged as a $b$-jet with probability $f_b$.
  %
  In order to be considered in the $b$-tagging algorithm,
  $b$-quarks inside the small-$R$ jet
  should satisfy $p_T \ge 15$ GeV.
  %
  The probability of tagging a jet is not modified
  if more than one $b$-quark is found among the jet constituents.

@@

    As in the case
    of small-$R$ jets, we only attempt to $b$-tag the two leading subjets,
    else one finds a degradation of the
    signal significance due to combinatorics.
    %
    The simulation of the fakes from light and charm jets
    is the same as in the small-$R$ jets.

@@

  An event with only one large-$R$, $b$-tagged, jet, which
  is assigned to be the leading Higgs candidate.
  %
  In addition, we require at least two small-$R$, $b$-tagged, jets,
  which must be separated with respect to the large-$R$ jet
  by an angular distance of $\Delta R\ge 1.2$.
  %

@@

Once a Higgs boson candidate has been identified,
its invariant mass is required to lie within a fixed window
around the nominal Higgs boson mass~\cite{Aad:2015zhl}.
%
In particular we require the condition
\be
\label{higgsmasswindow}
|m_{h,j} - 125| < 40~{\rm GeV} \, ,\, j=1,2 \, ,
\ee
where $m_{h,j}$ is the invariant mass of each of the two reconstructed  Higgs candidates.
%
This cut is substantially looser as the corresponding
cut used in the typical ATLAS and CMS $h\to b\bar{b}$
analyses~\cite{Aad:2012gxa,Chatrchyan:2013zna}: the motivation
for this choice is that the MVA will take care of the optimisation of this,
as well as of other cuts that are not explicitly performed.
%
Only events where the two Higgs candidates satisfy
Eq.~(\ref{higgsmasswindow}) are classified as signal events.
%

@@

%
In order to subtract the PU, a number of techniques
have been developed
recently~\cite{Cacciari:2009dp,TheATLAScollaboration:2013pia,Butterworth:2008iy,Cacciari:2007fd,Krohn:2009th,Krohn:2013lba,Ellis:2009me,Bertolini:2014bba,Cacciari:2014gra,Cacciari:2014jta,Berta:2014eza,Larkoski:2014wba}.\footnote{
These techniques have also important applications in the subtraction
of the UE/MPI contamination for jet reconstruction
in heavy ion collisions~\cite{Cacciari:2010te}.
}
%
In this work, PU  will be subtracted by means
of the {\tt SoftKiller} (SK)
method~\cite{Cacciari:2014gra}, as implemented in {\tt FastJet}.
%
The idea underlying {\tt SoftKiller} is based on eliminating particles
below a given cut-off in their transverse momentum, $p_T^{\rm (cut)}$, whose
value is dynamically determined in a way that makes the event-wide
transverse-momentum flow density $\rho$ vanish.
%
This $p_T$ flow density is defined as
\be
\rho\equiv{\rm median}_i \Bigg\{ \frac{p_{Ti}}{A_i}\Bigg\} \, ,
\ee
where the median is computed over all the patches $i$ with area
$A_i$ and transverse momentum $p_{Ti}$ in which the $\lp \eta,\phi\rp$ plane
is partitioned.
%
From its definition in terms of the median,
we observe that the value of $p_T^{(\rm cut)}$
will be dynamically raised until half of the patches have $\rho=0$.
%
The size and number of these patches is a free parameter of the algorithm -
here we will use square patches with length $a=0.4$.
%
We restrict ourselves to the central rapidity region,
$|\eta| \le 2.5$, for the estimation of the
$p_T$ flow density $\rho$.
%
In this analysis, {\tt SoftKiller} method is applied
to particles at the end of the parton shower, before
jet clustering.

>>>>

In this section we describe our analysis strategy.
%
First of all, we discuss the settings
for jet clustering  and the strategy for $b$-tagging.
%
Then we discuss the categorisation of events in different
topologies and how to prioritise among them.
%
We motivate our choice of analysis cuts by comparing signal and background
for representative kinematical distributions.
%
Finally, we describe the simulation of PU and validate
the PU subtraction strategy that we adopt.

@@

  These subjets are constructed by reclustering the constituents
  of a large-$R$ jet, again with  anti-$k_T$ algorithm,
  but this time with a smaller radius parameter, namely
  $R=0.3$~\cite{Aad:2015uka}.
 %
  These small-$R$ subjets will be the main input for
  $b$-tagging in the boosted category.
  %
  They are required to satisfy $p_T > 50$~GeV and $|\eta|<2.5$.
  %
\end{itemize}

In addition, we have
also explored the possible improvements
in the analysis from the use
of variable-$R$ jets~\cite{Krohn:2009zg}, finding
a similar performance as in the case of fixed-$R$ jets.
%
This is explained by the fact that
variable-$R$ jets are more suitable when
the degree of boost of the final state being reconstructed can span
a wide range~\cite{Cacciari:2008gd}, such as in heavy resonance
searches~\cite{Aad:2015fna},
where where the degree of boost of the final state
is {\it a priori} unknown.

@@

  %
  If a small-$R$ jet has at least one $b$-quark among their constituents,
  it will be tagged as a $b$-jet with probability $f_b$.
  %
  In order to be considered in the $b$-tagging algorithm,
  $b$-quarks inside the small-$R$ jet
  should satisfy $p_T \ge 15$ GeV~\cite{Aad:2015ydr}.
  %
  The probability of tagging a jet is not modified
  if more than one $b$-quark is found among the jet constituents.

@@

    As in the case
    of small-$R$ jets, we only attempt to $b$-tag the two leading subjets,
    else one finds a degradation of the
    signal significance due to combinatorics.
    %
    The treatment of the $b$-jet mis-identification
    from light and charm jets
    is the same as for the small-$R$ jets.

@@

  An event with exactly one large-$R$, $b$-tagged, jet, which
  is assigned to be the leading Higgs candidate.
  %
  In addition, we require at least two small-$R$, $b$-tagged, jets,
  which must be separated with respect to the large-$R$ jet
  by an angular distance of $\Delta R\ge 1.2$.
  %

@@

Once a Higgs boson candidate has been identified,
its invariant mass is required to lie within a fixed window
around the nominal Higgs boson mass $m_h\simeq 125$
GeV~\cite{Aad:2015zhl}.
%
In particular we require the condition
\be
\label{higgsmasswindow}
|m_{h,j} - 125| < 40~{\rm GeV} \, ,\, j=1,2 \, ,
\ee
where $m_{h,j}$ is the invariant mass of each of the two reconstructed  Higgs candidates.
%
This cut is substantially looser as the corresponding
cut used in the typical ATLAS and CMS $h\to b\bar{b}$
analyses~\cite{Aad:2012gxa,Chatrchyan:2013zna}: the motivation
for this choice is that the MVA will take care of the optimisation of this,
as well as of other cuts that are not explicitly performed.
%
Only events where the two Higgs candidates satisfy
Eq.~(\ref{higgsmasswindow}) are classified as signal events.
%

@@

%
In order to subtract the PU, a number of techniques
have been developed
recently~\cite{Cacciari:2009dp,TheATLAScollaboration:2013pia,Butterworth:2008iy,Cacciari:2007fd,Krohn:2009th,Krohn:2013lba,Ellis:2009me,Bertolini:2014bba,Cacciari:2014gra,Cacciari:2014jta,Berta:2014eza,Larkoski:2014wba}.\footnote{
These techniques have also important applications in the subtraction
of the UE/MPI contamination for jet reconstruction
in heavy ion collisions~\cite{Cacciari:2010te}.
}
%
In this work, PU  will be subtracted by means
of the {\tt SoftKiller} (SK)
method~\cite{Cacciari:2014gra}, as implemented in {\tt FastJet}.
%
This recently developed method has been shown to improve~\cite{Cacciari:2014gra} on the
performance of the commonly used area-based subtraction~\cite{Cacciari:2009dp}.
%

The idea underlying {\tt SoftKiller} is based on eliminating particles
below a given cut-off in their transverse momentum, $p_T^{\rm (cut)}$, whose
value is dynamically determined in a way that makes the event-wide
transverse-momentum flow density $\rho$ vanish.
%
This $p_T$ flow density is defined as
\be
\rho\equiv{\rm median}_i \Bigg\{ \frac{p_{Ti}}{A_i}\Bigg\} \, ,
\ee
where the median is computed over all the patches $i$ with area
$A_i$ and transverse momentum $p_{Ti}$ in which the $\lp \eta,\phi\rp$ plane
is partitioned.
%
From its definition in terms of the median,
we observe that the value of $p_T^{(\rm cut)}$
will be dynamically raised until half of the patches have $\rho=0$.
%
The size and number of these patches is a free parameter of the algorithm -
here we will use square patches with length $a=0.4$.
%
We restrict ourselves to the central rapidity region,
$|\eta| \le 2.5$, for the estimation of the
$p_T$ flow density $\rho$.
%
In this analysis, {\tt SoftKiller} method is applied
to particles at the end of the parton shower, before
jet clustering.

### 2015-12-07 paper/sec-conclusions.tex
More work on the paper

In this work, we have presented a detailed study of the feasibility
of the measurement of Higgs pair production in the $b\bar{b}b\bar{b}$
final state at the High-Luminosity LHC.
%
Our strategy is based on the combination of a traditional
cut-based analysis with modern multivariate analyses,
which allows improving the signal significance of this channel
as compared to previous studies.
%
Following a careful optimisation of the
signal reconstruction strategy for different event topologies,
we find that the highest significance is obtained
in the 
boosted category, while complementary information is also provided
by the intermediate and resolved categories.
%

Our analysis takes into account 
all relevant backgrounds, in particular
the dominant QCD multijets.
%
We include not only the irreducible $4b$ component, but
also the $2b2j$ and $4j$ backgrounds, which contribute
to the yield of reconstructed Higgs candidates
when light partons are mistagged as $b$-quarks.
%
We show that neglecting the contribution
from  fakes is a poor approximation, specially for the resolved and intermediate
categories.
%
The reason is that
the impact of fakes
can be substantially enhanced, when compared to a naive parton
level estimate, due to combinatorics and $b\bar{b}$
pair radiation during the parton shower.

A major difficulty in measurements involving relatively low $p_T$
jets at the HL-LHC is the large
amount of PU expected.
%
To account for this, we have simulated realistic PU conditions
and used the recently developed {\tt SoftKiller} method to reduce
the PU contamination.
%
We find that, especially in the boosted category, the impact of
PU after its subtraction is rather mild, and in particular the jet
substructure variables, which carry substantial
discrimination information, are reasonably robust against PU effects.

For a PU of $\la n_{\rm PU}\ra=150$, along what is expected
at the HL-LHC, our main result is that the combined
signal significance for the three categories is $S/\sqrt{B}\simeq 4.0$,
substantially improving previous studies.
%
Therefore, we conclude that, already from the $b\bar{b}b\bar{b}$
final state alone,
it should be possible to claim evidence for Higgs pair production at
the HL-LHC.
%
This  estimate for $S/\sqrt{B}$  could
be further enhanced,
in particular following an optimization of the PU subtraction
strategy.

One important implication of our study is that it should
be possible to improve  the accuracy on the extraction of
the Higgs trilinear coupling $\lambda$ from
a measurement of the
$\sigma\lp hh\to b\bar{b}b\bar{b}\rp$ cross-section, as compared
to existing estimates.
%
A determination of $\lambda$ in our approach would require
 however a substantial
 amount of work, involving
 not only regenerating signal samples
 for a wide range of values of  $\lambda$, but also
 repeating the analysis
optimisation, including the MVA training, for each
of these values.
%
This study is left to a future
publication, where we will also
compare with the corresponding  precision 
that has been obtained in other final states.
%
It will be in particular interesting to contrast
with the extraction of $\lambda$ from the
 $b\bar{b}\gamma\gamma$
and $b\bar{b}\tau\tau$ final states, that, while having
smaller rates as compared to $b\bar{b}b\bar{b}$,
benefit from reduced backgrounds.
%

@@

{\bf\noindent  Acknowledgments \\}
We thank R.~Contino, A.~Papaefstathiou and
G.~Salam for useful discussions on the topic
of Higgs pair production.
%
We thank E.~Vrodynou and M.~Zaro for assistance with di-Higgs production
  in {\tt MadGraph5\_aMC@NLO}.
%
  J.~R. is supported by an STFC Rutherford Fellowship and
  Grant ST/K005227/1 and ST/M003787/1.
%
J.~R. and N.~H. are
supported by an European Research Council Starting Grant ``PDF4BSM".
%
N.~B.~N. is supported by a PhD scholarship from the Malaysia
government.
%
K.~B. is supported by a studentships from the Rhodes Foundation.
%
J.~F. and C.~I. are supported by the STFC.

>>>>

In this work we have presented a detailed feasibility study for
 the measurement of Higgs pair production in the $b\bar{b}b\bar{b}$
final state at the High-Luminosity LHC with $\mathcal{L}=3$ ab$^{-1}$.
%
Our strategy is based on the combination of a traditional
cut-based analysis with state-of-the-art multivariate techniques,
leading to an improved signal significance 
as compared to previous studies.
%
Following a careful optimisation of the
signal reconstruction strategy for different event topologies,
we find that the highest significance is obtained
in the 
boosted category, while complementary information is also provided
by the resolved and (to a lesser extent) intermediate categories.
%

Our analysis takes into account 
all relevant backgrounds, in particular
the dominant QCD multijets.
%
We include not only the irreducible $4b$ component, but
also the $2b2j$ and $4j$ backgrounds, which contribute
to the yield of reconstructed Higgs candidates
when light and charm partons are mis-identified as $b$-quarks.
%
We show that neglecting the contribution
from  fakes is a poor approximation for all categories, the reason
being a combination of parton shower effects, with the associated $b$-quark
pair radiation, and selection requirements.

A major difficulty in measurements involving relatively low $p_T$
jets at the HL-LHC is the large
amount of PU expected.
%
To account for this, we have simulated realistic PU conditions
and used the recently developed {\tt SoftKiller} method to reduce
the PU contamination.
%
We find that, especially in the boosted category, the impact of
PU after its subtraction is rather mild, and in particular the jet
substructure variables, which carry substantial
discrimination information, are reasonably robust against PU effects.
%
For a PU environment with $\la n_{\rm PU}\ra=80$ we find that the combined
signal significance for the three categories is $S/\sqrt{B}\simeq 4.0$,
%
Therefore, we conclude that, already from the $b\bar{b}b\bar{b}$
final state alone,
it should be possible to claim evidence for Higgs pair production at
the HL-LHC.
%
This  estimate for $S/\sqrt{B}$  could
be further enhanced,
in particular following an optimization of the PU subtraction
strategy.

Our study indicates possible avenues that the LHC experiments
could explore to improve the signal significance of this
process.
%
One handle could be to reduce the contribution from light and charm
jet mis-identification, ensuring that the
$2b2j$ component is subdominant over the $4b$ background.
%
Another possibility would be to improve the mass resolution of the Higgs peak
in high-PU environments, since, as shown by the analysis without PU, this
distribution carries high discrimination power.
%
These and similar improvements
 might make possible an observation of Higgs pairs
in the $b\bar{b}b\bar{b}$ feasible even with only
$\mathcal{L}=300$ fb$^{-1}$.

One important implication of this work is that it might
be possible to improve  the accuracy on the extraction of
the Higgs trilinear coupling $\lambda$ from
a measurement of the
$\sigma\lp hh\to b\bar{b}b\bar{b}\rp$ cross-section, as compared
to existing estimates.
%
A determination of $\lambda$ in our approach would require
 however a substantial
 amount of work, involving
 not only regenerating signal samples
 for a wide range of values of  $\lambda$, but also
 repeating the analysis
optimisation, including the MVA training, for each
of these values.
%
This study is left to a future
publication, where we will also
compare with the corresponding  precision 
that has been obtained in other final states.
%
It will be in particular interesting to contrast
with the extraction of $\lambda$ from the
 $b\bar{b}\gamma\gamma$
and $b\bar{b}\tau\tau$ final states, that, while having
smaller rates as compared to $b\bar{b}b\bar{b}$,
benefit from reduced backgrounds.
%

@@

{\bf\noindent  Acknowledgments \\}
We thank R.~Contino, A.~Papaefstathiou and
G.~Salam for useful discussions on the topic
of Higgs pair production.
%
We thank E.~Vrodynou and M.~Zaro for assistance with di-Higgs production
  in {\tt MadGraph5\_aMC@NLO}.
%
  J.~R. is supported by an STFC Rutherford Fellowship and
  Grant ST/K005227/1 and ST/M003787/1.
%
J.~R. and N.~H. are
supported by an European Research Council Starting Grant ``PDF4BSM".
%
K.~B. is supported by a Rhodes Scholarship.
%
J.~F. and C.~I. are supported by the STFC.

### 2015-12-07 paper/sec-intro.tex
More work on the paper

Analogously to single Higgs production~\cite{Dittmaier:2012vm}, 
in the SM the dominant mechanism for the production of a pair of
Higgs bosons at the LHC is 
gluon fusion (see Ref.~\cite{baglio,Frederix:2014hta} and
references therein).
%
For a center-of-mass energy $\sqrt{s} = 14\,$TeV, the
next-to-next-to-leading order (NNLO)
total cross section is approximately $40\,$fb~\cite{deFlorian:2013jea},
which is increased by a further few percent once NNLL corrections
are accounted for~\cite{deFlorian:2015moa}.
%
Feasibility studies in the case of a SM-like Higgs boson
in gluon fusion have been performed for several different final states, including
$b\bar b\gamma\gamma$~\cite{Baur:2003gp,Barger:2013jfa},
$b\bar{b}\tau^+\tau^-$~\cite{Baur:2003gpa,Barr:2013tda,Dolan:2012rv,Dolan:2013rja},
$b\bar{b}W^+W^-$~\cite{Dolan:2012rv,Papaefstathiou:2012qe} and
$b\bar{b}b\bar{b}$~\cite{Baur:2003gpa,Dolan:2012rv,Wardrope:2014kya,deLima:2014dta,Barger:2013jfa}.
%
While these studies differ in their qualitative conclusions,
a consistent picture emerges 
that the ultimate precision in the determination of the Higgs trilinear
coupling $\lambda$
will only be achieved from the combination of various final states.

In addition to the gluon-fusion production mode, Higgs pairs
can also be produced in the vector-boson fusion
channel $hhjj$~\cite{Contino:2010mh,Dolan:2013rja,Dolan:2015zja,
  Brooijmans:2014eja},
the associated production modes $hhW$ and $hhZ$~\cite{Barger:1988jk,baglio}
(also known as Higgs-Strahlung),
and also in association
with top quark pairs $hht\bar{t}$~\cite{Englert:2014uqa}.
%
All these channels are challenging due to the small production
rates: at 14 TeV, the inclusive total cross-sections are
2 fb for VBF $hhjj$~\cite{Liu-Sheng:2014gxa},
0.5 fb for $W(Z)hh$~\cite{baglio}
and 1.0 for $hht\bar{t}$~\cite{Englert:2014uqa}.
%
Concentrating on the SM dynamics of Higgs pair production
in different channels, several studies
have investigate the interplay of various kinematical
distributions towards the optimisation of the
extraction of $\lambda$ from the measured
cross-sections, as well as the improvement
in the signal modeling taking into account
higher-order corrections and theoretical
uncertainties~\cite{Slawinska:2014vpa,Chen:2014xra,Goertz:2013kp,
  Frederix:2014hta,Dawson:2015oha,Maltoni:2014eza,Maierhofer:2013sha,Grigo:2013rya,Grigo:2014jma}.
%

While the SM production rates for Higgs
pair production are small in all production modes,
and require the full integrated luminosity of the HL-LHC phase
to be accessed, double Higgs production rates can be substantially
enhanced in a variety of Beyond the SM (BSM) scenarios.
%
Feasibility studies of Higgs pair production in New Physics
models have been performed in a number of different frameworks,
including Effective Field
Theories (EFTs) with higher-dimensional
operators and anomalous values of the
Higgs couplings~\cite{Nishiwaki:2013cma,Dall'Osso:2015aia,Azatov:2015oxa,Liu:2014rba,Goertz:2014qta,He:2015spf,Grober:2015cwa}, resonant production
in models such as extra dimensions~\cite{Gouzevitch:2013qca,Cooper:2013kia,No:2013wsa}, as well as
in the context of Supersymmetry or Two Higgs Doublet models (2HDMs)~\cite{Belyaev:1999kk,Han:2013sga,Hespel:2014sla,Wu:2015nba,Cao:2014kya,Ellwanger:2013ova}.

%
In many of these scenarios, the production rates are enhanced
and Higgs pair production becomes accessible already at
Run II, while still being consistent with current limits on BSM searches
and single Higgs coupling measurements.
%
With this motivation, searches for the production of Higgs pair
have already been performed at Run I
by ATLAS in the $b\bar{b}b\bar{b}$~\cite{Aad:2015uka}
and $b\bar{b}\gamma\gamma$~\cite{Aad:2014yja} final states,
and by
CMS in the same $b\bar{b}b\bar{b}$~\cite{Khachatryan:2015yea}
and $b\bar{b}\gamma\gamma$~\cite{Chatrchyan:2011wt} final
states.
%
One should note that in general BSM dynamics modify substantially
the kinematic distributions of the Higgs decay products, for
instance boosting the di-Higgs system, and therefore
different analysis strategies would be requires in BSM
Higgs pair searches as compared to SM production measurements.

@@

The structure of this paper is the following.
%
In Sect.~\ref{mcgeneration} we discuss the modeling of the signal
and background processes using Monte Carlo event generators.
%
In Sect.~\ref{sec:analysis}
we introduce our analysis strategy, and in particular
the classification of each individual event into
different categories according to their topology.
%
The results for the traditional cut-based analysis
are presented in Sect.~\ref{sec:results}, and in
Sect.~\ref{sec:mva} we show how we can enhance signal
significance using multivariate techniques.
%
The robustness of our results under realistic pile-up
conditions expected at the HL-LHC is illustrated in
....
%
Finally, in Sect.~\ref{sec:conclusions} we conclude and outline
how our results can be extended to estimate the accuracy
in the determination of trilinear coupling $\lambda$ and the constraints on
BSM scenarios.

>>>>

Analogously to single Higgs production~\cite{Dittmaier:2012vm}, 
in the SM the dominant mechanism for the production of a pair of
Higgs bosons at the LHC is 
gluon fusion (see Ref.~\cite{baglio,Frederix:2014hta} and
references therein).
%
For a center-of-mass energy $\sqrt{s} = 14\,$TeV, the
next-to-next-to-leading order (NNLO)
total cross section is approximately $40\,$fb~\cite{deFlorian:2013jea},
which is increased by a further few percent once
next-to-next-to-leading logarithmic
(NNLL) corrections
are accounted for~\cite{deFlorian:2015moa}.
%
Feasibility studies in the case of a SM-like Higgs boson
in gluon fusion have been performed for several different final states, including
$b\bar b\gamma\gamma$~\cite{Baur:2003gp,Barger:2013jfa},
$b\bar{b}\tau^+\tau^-$~\cite{Baur:2003gpa,Barr:2013tda,Dolan:2012rv,Dolan:2013rja},
$b\bar{b}W^+W^-$~\cite{Dolan:2012rv,Papaefstathiou:2012qe} and
$b\bar{b}b\bar{b}$~\cite{Baur:2003gpa,Dolan:2012rv,Wardrope:2014kya,deLima:2014dta,Barger:2013jfa}.
%
While these studies differ in their qualitative conclusions,
a consistent picture emerges 
that the ultimate precision in the determination of the Higgs trilinear
coupling $\lambda$
will only be achieved from the combination of various final states.

In addition to the gluon-fusion production mode, Higgs pairs
can also be produced in the vector-boson fusion
channel $hhjj$~\cite{Contino:2010mh,Dolan:2013rja,Dolan:2015zja,
  Brooijmans:2014eja},
the associated production modes
$hhW$ and $hhZ$~\cite{Barger:1988jk,baglio,Cao:2015oxx}
(also known as Higgs-Strahlung),
and also in association
with top quark pairs $hht\bar{t}$~\cite{Englert:2014uqa}.
%
All these channels are challenging due to the small production
rates: at 14 TeV, the inclusive total cross-sections are
2 fb for VBF $hhjj$~\cite{Liu-Sheng:2014gxa},
0.5 fb for $W(Z)hh$~\cite{baglio}
and 1.0 for $hht\bar{t}$~\cite{Englert:2014uqa}.
%
Concentrating on the SM dynamics of Higgs pair production
in different channels, several studies
have investigate the interplay of various kinematical
distributions towards the optimisation of the
extraction of $\lambda$ from the measured
cross-sections, as well as the improvement
in the signal modeling taking into account
higher-order corrections and theoretical
uncertainties~\cite{Slawinska:2014vpa,Chen:2014xra,Goertz:2013kp,
  Frederix:2014hta,Dawson:2015oha,Maltoni:2014eza,Maierhofer:2013sha,Grigo:2013rya,Grigo:2014jma}.
%

While the SM production rates for Higgs
pairs are small,
and require the full integrated luminosity of the HL-LHC
to be accessed, double Higgs production rates can be substantially
enhanced in a variety of Beyond the SM (BSM) scenarios.
%
Feasibility studies of Higgs pair production in New Physics
models have been performed in a number of different frameworks,
including Effective Field
Theories (EFTs) with higher-dimensional
operators and anomalous values of the
Higgs couplings~\cite{Nishiwaki:2013cma,Dall'Osso:2015aia,Azatov:2015oxa,Liu:2014rba,Goertz:2014qta,He:2015spf,Grober:2015cwa}, resonant production
in models such as extra dimensions~\cite{Gouzevitch:2013qca,Cooper:2013kia,No:2013wsa}, as well as
in the context of Supersymmetry or Two Higgs Doublet models (2HDMs)~\cite{Belyaev:1999kk,Han:2013sga,Hespel:2014sla,Wu:2015nba,Cao:2014kya,Ellwanger:2013ova}.
%
In general, BSM dynamics modify
the kinematic distributions of the Higgs decay products, for
instance boosting the di-Higgs system, and therefore
different analysis strategies would be required in BSM
Higgs pair searches as compared to SM production measurements.

Searches for the production of Higgs pairs
have already been performed at Run I with 8 TeV
by ATLAS in the $b\bar{b}b\bar{b}$~\cite{Aad:2015uka}
and $b\bar{b}\gamma\gamma$~\cite{Aad:2014yja} final states,
and by
CMS in the same $b\bar{b}b\bar{b}$~\cite{Khachatryan:2015yea}
and $b\bar{b}\gamma\gamma$~\cite{Chatrchyan:2011wt} final
states.
%
%
In addition, ATLAS has presented~\cite{Aad:2015xja} a combination
of its di-Higgs searches in the $bb\tau\tau,$
$\gamma\gamma WW^*$, $\gamma\gamma bb$, and $bbbb$ final states.
%
Many other exotic searches involves Higgs pairs in the final
state, such as the recent
CMS searches for a heavy Higgs boson $H$~\cite{Khachatryan:2015tha}.

@@

The structure of this paper is the following.
%
In Sect.~\ref{mcgeneration} we discuss the modeling of the signal
and background processes using Monte Carlo event generators.
%
In Sect.~\ref{sec:analysis}
we introduce our analysis strategy, and in particular
the classification of each individual event into
different categories according to their topology.
%
The results for the traditional cut-based analysis
are presented in Sect.~\ref{sec:results}.
%
In Sect.~\ref{sec:mva} we show how we can enhance signal
significance using multivariate techniques, and
illustrate the robustness of our results under realistic pile-up
conditions expected at the HL-LHC.
%
Finally, in Sect.~\ref{sec:conclusions} we conclude and outline
how our results can be extended to estimate the accuracy
in the determination of trilinear coupling $\lambda$ and the constraints on
BSM scenarios.
